%-------------------------
% Resume in Latex
% Author : Neelansh Khare
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\titlespacing*{\section}{0pt}{1\baselineskip}{0.75\baselineskip}
\begin{document}


\begin{center}  
    \textbf{\Huge \scshape Neelansh Khare} \\ \vspace{1pt}
    \color{blue}
    \small \href{tel:19499926803}{{+1 949-992-6803}} $|$ \href{mailto:kharen@uci.edu}{{kharen@uci.edu}} $|$ 
    \href{https://linkedin.com/in/neelansh-khare}{{linkedin.com/in/neelansh-khare}} $|$
    \href{https://github.com/Neelansh-Khare}{{github.com/Neelansh-Khare}} $|$
    \href{https://neelanshkhare.notion.site/d518ba0af3604c1189da03c6ab047f3c}{{Neelansh's website}} 
\end{center}

%-----------Objective-----------
\section{Objective}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{}{Aspiring to secure a Summer 2024 software engineering internship where I can apply my passion for AI/ML, Quantitative finance, Data science, and Full-stack development. Equipped with a strong foundation in computer science, hands-on experience in application development, and a keen interest in working in the fields of technology and business. Eager to contribute on innovative projects and solve complex problems in a dynamic team environment.} \\
  }}
  \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California - Irvine}{Irvine, CA}
      {Bachelor of Science in Computer Science}{Expected March 2025}
      \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{Relevant Coursework: }{Intro to Artificial Intelligence, Data Structures and Algorithims, System Design, Data Management, Computer Vision, Software Engineering, Software Testing, Analysis, and Quality Assurance} \\
         \textbf{Awards: }{Dean’s Honor List}\\
         \textbf{Extracurriculars: }{Software Developer for ICSSC, Event Coordinator for the Indian Subcontinent Club (ISC), Intern for ASUCI, Volunteer for ENGin, Philanthropy Chair for Sigma Pi, Ex Board Member for Legacy Robotics/UCI Fits 
         }\\
        }}
        \end{itemize}
  \resumeSubHeadingListEnd
  


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{June 2022 -- Present}
      {University of California, Irvine}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Engineered a Java application to automate manual processes, achieving a 90\% reduction in task completion time.}
        \resumeItem{Built a Java web scraping tool using RESTful APIs for quicker onboarding through generated documentation.
        }
        \resumeItem{Utilized Java, React, JavaScript, SQL, Git, Gradle, Spring, Maven, Excel, JUnit, OOP, and Atlassian Suite to complete 75+ Jira tasks for frontend, backend, testing and database tickets on a financial web-application. 
        }
      \resumeItemListEnd
    \resumeSubheading
      {Research}{January 2024 -- Present}
      {He Lab, University of California, Irvine}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Worked on predicting the movement of nano particles using OpenCV, and PyTorch.}
        \resumeItem{Fine-tuned an electron microscopy neural network to fit our needs.
        }
        \resumeItem{Created an algorithim to generate new sample data to test our model. 
        }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
      {\textbf{Python Based Applications} $|$ \emph{Python, PyGame, NumPy, Matplotlib, REST APIs, OpenCV, Sockets}}{}
        \resumeItemListStart
          \resumeItem{Created a Python script for stock tracking and automated, risk-averse sales using Bard AI and Schwab APIs.}
          \resumeItem{Built an app with OpenCV and Matplotlib for recognizing individuals, household items and visualizing results.}
          \resumeItem{Created playable versions of 2048, ConnectFour, and Columns using PyGame, NumPy, Sockets, and more.}
          \resumeItem{Built Discord bots for engagement-boosting games, resulting in a 70\% increase in engagement.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Full Stack Development} $|$ \emph{JavaScript, Java, MongoDB, React, WordPress, HTML, CSS, REST APIs, AppScript, Svelte}}{}
          \resumeItemListStart
            \resumeItem{Helped develop 2 full-stack club/stealth startup websites with Java backend, Svelte/React frontend, and MongoDB.}
            \resumeItem{Integrated PayPal API and implemented Google Sheets AppScript macros for data-related automations.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Upkey Professional Development Workshop} $|$ \emph{Kotlin, Figma}}{}
          \resumeItemListStart
          \resumeItem{Led a team to 3rd place with a full stack Java mobile app pitch that worked to find on to go gym solutions.}
          \resumeItem{Utilized Kotlin for app development, with Figma for design.}
          \resumeItemListEnd

\resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks: }{Proficient in Python, Java, JavaScript, React, SQL, C++, R, Git, Excel, Gradle, Maven. Familiar with ROS2, OpenCV, Node.js, AWS, TensorFlow, MongoDB, Kotlin.
     } \\
     \textbf{Developer Tools/Skills: }{Visual Studio Code, Eclipse, IntelliJ, IDLE, GitHub, Python Tutor, Excel, Atlassian Suite, BlueJ, SQL Server, Android Studio, Figma, Agile, CI/CD, Unit Testing} \\
     \textbf{Soft Skills: }{Great communication skills, proficient at working under pressure, dependable, able to work in a team, willingness to learn, adaptability}\\
     \textbf{Other Interests: }{Automation, Computer Vision, Crypto, Web3, QA, cybersecurity, product management, UI/UX, Virtual/Augmented Reality, Cloud computing, app development}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
